Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.tex

To formalize these observations, we fit a generalized linear model to
the proportion of faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p =0.89). We found the same pattern of results
for the OpenPose face detections, omitted here for brevity. We also
found the same pattern with respect to infant's visual access to hands
(see Table 4); including interaction terms also reduced any main effect
of age on the proportion of hands detected (b = -15.7, SE = 113.98, z =
-0.14 , p =0.89). Thus, these results suggest that infants' access to
social information is heavily influenced by their postural and
locomotive development.

@@

Finally, we analyzed how face and wrists detections changed during
object labeling events as a function of infant's posture and
orientation. Specfically, we analyzed a four-second window around each
labeling event (e.g., ``Look at the {[}zem{]}!''); these labeling events
were hand-annotated and automatically synchronized with the
frame-by-frame face detections. We again found that infants' posture and
orientations impacted the degree to which they saw their caregiver's
face and wrist during a labeling event; infants who were sitting or
standing were more likely to have access to this social information.

@@

We used a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and wrists that were avaliable in the child's visual field. Thus,
infants' postural and locomotive developments are mediating factors that
explain some of the age-related changes in the proportion of faces and
hands avaliable in infants' visual field. Broadly, this work suggests
that motoric developments mediate how infants experience their visual
world and the social information in it: infants that are sitting and
standing have a different view of their world, the people in it, and the
actions that are being performed.

This work also deploys novel advancements in computer vision to the
study of developmental psychology. The field of object detection and
recognition has advanced dramatically in the past five years since the
re-birth of deep learning algorithms (Krizhevsky, Sutskever, \& Hinton,
2012), creating a new generation of algorithmic tools. These tools are
substantially better equipped to deal with noisier, more complicated
datasets and can extract richer and more detailed information. Videos
from the infant perspective provided substantial challenges (e.g.,
partially occluded faces) for the classic models of face detection
(e.g., ViolaJones) (Viola \& Jones, 2004). Further, as the headcam
technologies employed here were inexpensive (\textasciitilde{}\$60 a
camera) and the computer vision algorithms freely avaliable, this method
is a promising avenue for quanitfying the visual and social information
avaliable to infant learners.

Thus, we suggest that the combined use of these new tools can be
leveraged to understand the changing infant perspecive on the visual
world and the implications of these changes for both linguistic,
cognitive, and social development.

>>>>

To formalize these observations, we fit a generalized linear model to
the proportion of faces infants saw in each posture and orientation (as
detected by MTCNN), with participant's age, orientation, and posture as
independent variables. A summary of the coefficients of a model with
only main effects (and no interactions) model can be found in Table 3.
When we did include interaction terms between age, posture, and
orientation, age no longer remained a significant predictor (b = -15.84,
SE = 113.98, z = -0.14 , p = 0.89). We found the same pattern of results
for the OpenPose face detections, omitted here for brevity. We also
found the same pattern with respect to infant's visual access to hands
(see Table 4); including interaction terms also eliminated any main
effect of age on the proportion of hands detected (b = -15.7, SE =
113.98, z = -0.14 , p = 0.89). Thus, these results suggest that infants'
access to social information is heavily influenced by their postural and
locomotive development.

@@

Finally, we analyzed how face and wrist detections changed during object
labeling events as a function of infant's posture and orientation.
Specfically, we analyzed a four-second window around each labeling event
(e.g., ``Look at the {[}zem{]}!''); these labeling events were
hand-annotated and automatically synchronized with the frame-by-frame
face detections. We found that infants' posture and orientations
impacted the degree to which they saw their caregiver's face and wrist
during a labeling event; infants who were sitting or standing were more
likely to have access to this social information. However, this did not
manifest in a direct change the presence of wrists/hands before
vs.~after naming events (average difference in proportion of wrists
detected, 8 m.o. = -0.006,12 m.o. = -0.013 ,16 m.o. = -0.007 ) or in
proportion of faces detected (average difference in proportion of faces
detected, 8 m.o. = -0.002,12 m.o. = 0 ,16 m.o. = -0.004 ).

@@

We used a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and wrists that were available in the child's visual field. Thus,
infants' postural and locomotive developments are mediating factors that
explain some of the age-related changes in the proportion of faces and
wrists/hands that are visually available to infants. Broadly, this work
suggests that motoric developments mediate how infants experience their
visual world and the social information in it: infants that are sitting
and standing have a different view of their world, the people in it, and
the actions that are being performed.

This work also deploys novel advancements in computer vision to the
study of developmental psychology. The field of object detection and
recognition has advanced dramatically in the past five years since the
re-birth of deep learning algorithms (Krizhevsky, Sutskever, \& Hinton,
2012), creating a new generation of algorithmic tools. These tools are
substantially better equipped to deal with noisier, more complicated
datasets and can extract richer and more detailed information. Videos
from the infant perspective provided substantial challenges (e.g.,
partially occluded faces) for the classic models of face detection
(e.g., ViolaJones) (Viola \& Jones, 2004). Further, as the headcam
technologies employed here were inexpensive and the computer vision
algorithms freely available, this method is a promising avenue for
quantifying the visual and social information available to infant
learners.

Broadly, we suggest that the combined use of these new tools can be
leveraged to understand the changing infant perspective on the visual
world and the implications of these changes for linguistic, cognitive,
and social development.
